Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-06 ms.tex
conclusions 5

  \begin{enumerate}
  \item A stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
    outward wind. In steady-state the gas inflow rate towards the black hole is proportional to the
    stellar mass enclosed inside of $\rs$.  In the limit of strong heating, the stagnation radius resides close to the Bondi radius (eq.~[\ref{eq:rbondi}]).  
  \item The location of the stagnation radius, and hence the SMBH accretion rate, is a sensitive function of the gas heating rate $\propto v_w^{2}$.  Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the star formation history in the galactic nuclear region.  A recent star burst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for an exclusively old stellar population, mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.  Ongoing, continuous star formation presents a hybrid situation: energy input is usually dominated by young stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).

@@

>>>>

  \begin{enumerate}
  \item A stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
    outward wind. In steady-state the gas inflow rate towards the black hole is proportional to the
    stellar mass enclosed inside of $\rs$.  In the limit of strong heating, the stagnation radius resides interior to the SMBH influence radius and coincides with the Bondi radius (eq.~[\ref{eq:rbondi}]).  In the limit of weak heating ($\zeta < \zeta_c$; eq.~[\ref{eq:zetac}]), the stagnation radius moves to large radii, near or exceeding the stellar break radius $r_b \gg r_{\rm inf}$.

\item The inclusion of thermal conduction results in only moderate changes to the key properties of the flow (e.g. stagnation radius, mass accretion rate, and thermal stability) for causal values of the saturation parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).

  \item The location of the stagnation radius, and hence the SMBH accretion rate, is a sensitive function of the gas heating rate $\propto v_w^{2}$.  Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the star formation history in the galactic nuclear region.  A recent star burst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for an exclusively old stellar population, mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.  Ongoing, continuous star formation presents a hybrid situation: energy input is usually dominated by young stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).

@@

\section*{Acknowledgments}
We acknowledge helpful conversations with Jerry Ostriker, Eliot Quataert, ....  BDM gratefully acknowledges support from NASA {\it Fermi} grant NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan Foundation.
